Testing atlantisom: visualize weight at (st)age output. How shall we interplolate this for true ages?

### 2019-05-16 TestWeightAtStage.Rmd
add CCA examples

We should get the upper end of Greenland halibut with a 200cm max length bin. That shouldnt matter for weight at age.

@@

```
```{r vis-wtageclass-test3}

@@

```
```{r vis-wtageclass-test4}

@@

There are some interesting jumps between age classes. Most pronounced for herring, but those are real age classes!

@@

wageplot <- ggplot(wtage_annsurv, aes(time, atoutput)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (5 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year survey"))

@@

Here we check the CCA model (Atlantis Summit Common Scenario 1) saved length and weight census output for small species at Isaac's suggestion:

@@

Sardine:
```{r plotCCAsardine, eval=FALSE}
ss_length_censussurvsamp <- length_censussurvsamp$muweight %>%
  filter(species == "Pacific_sardine")

lfplot <- ggplot(ss_length_censussurvsamp, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte() +
  labs(subtitle = paste(scenario.name, ss_length_censussurvsamp$species))

lfplot
```

Anchovy:
```{r plotCCAanchovy, eval=FALSE}
ss_length_censussurvsamp <- length_censussurvsamp$muweight %>%
  filter(species == "Anchovy")

lfplot <- ggplot(ss_length_censussurvsamp, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte() +
  labs(subtitle = paste(scenario.name, ss_length_censussurvsamp$species))

lfplot
```

Herring:
```{r plotCCAherring, eval=FALSE}
ss_length_censussurvsamp <- length_censussurvsamp$muweight %>%
  filter(species == "Herring")

lfplot <- ggplot(ss_length_censussurvsamp, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte() +
  labs(subtitle = paste(scenario.name,ss_length_censussurvsamp$species))

lfplot
```

How do these three look?

Do we need to change something about the length comp estimation?

>>>>

We should get the upper end of Greenland halibut with a 200cm max length bin. That shouldnt matter for weight at age. This is all timesteps for each species by agecl.

@@

```{r vis-wtageclass-test3}

@@

```{r vis-wtageclass-test4}

@@

There are some interesting jumps between age classes. Most pronounced for herring. All of these species would be split into two true ages per age class. Interpolation could be interesting.

@@

# reverse to show agecl time series of wt
wageplot <- ggplot(wtage_annsurv, aes(time, atoutput)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (5 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year survey"))

@@

Here we check the CCA model (Atlantis Summit Common Scenario 1) saved length and weight census output for small species at Isaac's suggestion (all three of the following are true age classes, NumAgeClassSize=1 per Atlantis agecl bin:

@@

Sardine:
```{r plotCCAsardine, eval=FALSE}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Pacific_sardine")

wageplot <- ggplot(censuswt, aes(time, atoutput)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (1 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year survey"))

wageplot + facet_wrap(c("species"), scales="free_y")
```

Anchovy:
```{r plotCCAanchovy, eval=FALSE}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Anchovy")

wageplot <- ggplot(censuswt, aes(time, atoutput)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (1 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year survey"))

wageplot + facet_wrap(c("species"), scales="free_y")
```

Herring:
```{r plotCCAherring, eval=FALSE}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Herring")

wageplot <- ggplot(censuswt, aes(time, atoutput)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (1 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year survey"))

wageplot + facet_wrap(c("species"), scales="free_y")
```

How do these three look? Herring had a rough period from model years 15-30 or so.

Now for some CCA groups with multiple true ages per stage.

Pacific hake, 2 true ages per class:
```{r plotCCAhake, eval=FALSE}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Mesopel_M_Fish")

wageplot <- ggplot(censuswt, aes(time, atoutput)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (1 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year survey"))

wageplot + facet_wrap(c("species"), scales="free_y")
```

Bocaccio rockfish, 5 true ages per age class:
```{r plotCCAbocaccio, eval=FALSE}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Bocaccio_rockfish")

wageplot <- ggplot(censuswt, aes(time, atoutput)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (1 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year survey"))

wageplot + facet_wrap(c("species"), scales="free_y")
```

Yelloweye rockfish, most extreme at 12 true ages per age class:
```{r plotCCAYelloweye, eval=FALSE}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Yelloweye_rockfish")

wageplot <- ggplot(censuswt, aes(time, atoutput)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (1 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year survey"))

wageplot + facet_wrap(c("species"), scales="free_y")
```

I'm not sure any of this helps us decide how to interpolate, but there is clearly contrast in weight at age (class) in both models and example runs.
